---
title: "Windmill HW 1"
author: "Ethan Kemeny"
date: "9/19/2018"
output: html_document
---

```{r}
library(tidyverse)
windmills <- read.table("Windmill.txt", header = TRUE)
```

1. It can be costly to produce windmills.  Companies often will use reference sites as an indicator of how efficient a canadite site will be.  Using the data we will determine how good of a predictor reference sites are, as well as be able to predict canadate site speeds using the reference speeds.  Using statistical modeling, we can produce quanitittive estimates and be able to better understand the actueal relationship between reference and canadite sites.


2.
```{r}

ggplot(windmills, aes(RSpd,CSpd)) + geom_point() +geom_smooth(se = FALSE) + annotate("text", x = 5,y = 20, label = "paste(italic(R) ^ 2, \" =\")", parse =  TRUE) + annotate("text", x=7,y =19.8, label =cor(windmills$RSpd,windmills$CSpd), parse = TRUE )


```

  The correlation is 0.76 which implies a relatively strong, positive relationship between the speed. As the reference speed increases so does the canadite site speed. Most of the speeds found at reference sites are below 15, which would mean there are potential outliers for speeds greater than 15. Throughout the graph, even though there are less data points after a reference speed of 15, the variation appears to be approximately the same throughout.


3.
$y_i = \beta_0 + \beta_1x_i$
$y_i$ is the speed of the $i^{th}$ candidate site. 
$x_i$ is the speed of the $i^{th}$ reference site.
If the speed at a reference site is 0, then $\beta_0$ is the expected speed of the candidate site.
For every increase in 1 unit of speed for the reference site, the candidate site is expected to change by $\beta_1$ units of speed.
In order to use this simple linear regression model, we are assuming that the relationship between reference and candidate speed is linear, the candidate speeds are independent of each other, the data points are normally distributed about the regression line, and the variation of the residuals is equal across the regression line. 
